%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}{\slshape
    "A self-organizing system acts autonomously, as if the interconnecting  \\
    components had a single mind. And as these components spontaneously\\
    march to the beat of their own drummer, they organize, adapt,\\
    and evolve toward a greater complexity than one would ever\\
    expect just by looking at the parts by themselves."} \\ \medskip
    --- \defcitealias{samuels_defense_2013}{L. K. Samuels}\citetalias{samuels_defense_2013} \citep{samuels_defense_2013}
\end{flushright}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
   I would like to thank everyone who has graciously provided me with their support and validation through the entire process of writing this thesis. Thank you to Srinivas Gorur-Shandilya, who made all of this possible and encouraged me to pursue this, despite everything. Thank you to Eve Marder who took me in and, without asking, re-arranged my life and education in ways I will forever be grateful for.
   
   I could not have done this without my family, either. Thank you to Sophia, Bobby, Nikki, Miles, Hayden, and Cam. And finally, thank you to my chosen family. Thank you to everyone who has spent countless hours with me talking and philosophizing about science and the world, to everyone who has pushed me to be better than I am now, and most importantly, made the choice to love and support me in ways I will forever remember and be grateful for.

\bigskip

%\noindent\emph{Regarding \mLyX}: The \mLyX\ port was intially done by
%\emph{Nicholas Mariette} in March 2009 and continued by
%\emph{Ivo Pletikosi\'c} in 2011. Thank you very much for your
%work and for the contributions to the original style.


\endgroup
